\title{A Night at Zonix: An Office Roleplay Adventure}
\course{DATT 4310}
\author{Sina Karimi\\Student ID: 216863631}
\date{\today}


\maketitle
\newpage

\section*{Introduction}
In a simulated corporate world, I found myself immersed in a unique role-playing game set within the confines of the fictional company Zonix. Assigned the character of Rowan Salvatore, an aloof and self-centered vampire, I embarked on a journey through the office setting of Night Team Kentucky. With personal goals intertwined with the dynamics of the game, I navigated through encounters, challenges, and unexpected twists, gaining insights into both the game mechanics and my character's motivations.

\section*{Character Goals}
As Rowan Salvatore, my primary objective was twofold: to seek potential targets for vampiric transformation and to fulfill familial obligations by finding prey for my brother's initiation into the family vampire heritage. This quest for self-preservation and family legacy drove my interactions within the game. \\

Initially, I roamed the office corridors, observing and assessing potential targets for vampiric conversion. However, my exploration took an unexpected turn when I encountered individuals offering drugs, leading me down a path of susceptibility to external influences. Entranced by the allure of "listening to magic," I found myself manipulated into a trance-like state, diverting from my original objectives.\\

Subsequently, I was subjected to a polymorphing spell, transforming me into a zombie beholden to a mysterious master's commands. Despite this setback, my determination remained unwavering as I adhered to my master's directives, culminating in attendance at a summoning ritual, albeit in an altered form.\\

In a pivotal moment towards the game's conclusion, I attempted to assert dominance by casting fear upon a wall of adversaries. However, my efforts were thwarted as my vampiric intimidation failed, underscoring the limitations of my character's abilities within the game's mechanics.\\

\section*{Impressions}
Engaging in the Zonix Inc. role-playing experience was a refreshing departure from typical gaming setups. Mixing corporate dynamics with fantastical elements provided a fresh perspective on character development and interpersonal interactions.

Upon reflection, I noticed my tendency to follow a linear storyline with my character, which limited my exploration of alternative strategies. Despite this, I found myself captivated by the immersive nature of the game, overcoming my initial skepticism toward RPGs.

Overall, delving into the Zonix office roleplay was a blast. Despite struggling to deviate from a single character path, I thoroughly enjoyed the experience. It was surprising how engaging it was, considering RPGs aren't usually my thing.
